---
format:
  pdf:
    tbl-cap-location: top
    dpi: 500
    fig-pos: "H"
    number-sections: true
    cite-method: natbib
    include-in-header: preamble.tex
    include-before-body: title.tex
pdf-engine: xelatex
monofont: "DejaVu Sans Mono"
mainfont: "Times New Roman"
execute: 
  echo: false
  warning: false
editor: source
bibliography: references.bib
biblio-style: apalike
natbiboptions: round
link-citations: true
linkcolor: blue!000!black
urlcolor: blue!000!black
citecolor: blue!000!black
linestretch: 1.5
indent: TRUE
---

```{r}
#| label: setup
#| include: false
options(scipen=999)
knitr::opts_chunk$set(
                      fig.pos = "H", 
                      fig.env= 'figure', 
                      ft.align = "left",
                      ft.tabcolsep= 0, 
                      ft.latex.float = "none",
                      ft.arraystretch = 0.3
                      )
library(tidyverse)
library(readr)
library(readxl)
library(zoo)
library(magick)
library(stringi)
library(patchwork)
library(xtable)
library(scales)
library(rvest)
library(rebus)
library(PNWColors)
library(lubridate)
library(here)
library(flextable)
library(gt)
library(officer)
library(officedown)
library(modelsummary)
library(sandwich)
library(lmtest)
library(stargazer)
```

```{r}
#| label: func
source(here("Functions","flextable_word.R" ))
source(here("Functions","modelsummary_pdf.R" ))
source(here("Functions","borderlines.R" ))

set_flextable_defaults(font.size = 7, 
                       text.align = "left", 
                       font.color = "black", 
                       theme_fun = theme_apa, 
                       padding = 0,
                       line_spacing = 0)
```

# TO DO
- change the footers for all tables


# Introduction

@duygun2021


# Literature Review

#  Data and Methodology

The analysis utilises Kenneth French's 49 industry portfolio returns^[\url{http://mba.tuck.dartmouth.edu/pages/faculty/ken.french}]. Through his website Kenneth French provides a variety of financial market related data for research purposes, which include the famous Fama/French factors data. These data have two main advantages for researchers. First, the industry portfolio data varies in detail from 5 to 49 industry data-sets. Second, the data cover long periods of time, typically to pre World War II. Specifically, the daily data covers the period 1 July 1926 to 29 July 2022. The significant length and breadth of this data is essential for our analysis.   

We create 5 industry groups from the 49 industries in order to calculate the cross sectional dispersions as outlined in the methodology. In the data, stocks are assigned^[At the end of June each year] from the NYSE, AMEX, NASDAQ to an industry portfolio using a four-digit Centre for Research in Security Prices Standard Industry Classification Codes (CSRP-SIC). Essentially, the CSRP-SICs determine the level of industry aggregation in the data. Therefore, in @tbl-grouping we group the industries using the CSRP-SICs^[These are also available from \url{http://mba.tuck.dartmouth.edu/pages/faculty/ken.french}]. Lastly, @fig-cons to @fig-mines, and @tbl-desc show the described industry data. 


Empirically herding is defined in line with @chang2000examination. Herding is measured by first calculating returns:

$$ R_{t} = \left(\dfrac{E_t}{E_{t-1}} - 1\right) \times 100,$$


where $R_{t}$ is a return at time $t$, $E_t$ and $E_{t-1}$ is index value at time $t$ and $t-1$. Returns form the foundation of the analysis as they contain all information on the market, including shocks and investor sentiment. 

**Following @christie1995following and @chang2000examination we calculate two dispersion metrics. The cross-sectional absolute standard deviations ($CSAD_{t}$)**. **add** The dispersion measures are calculated for all markets as follows:


$$CSAD_{t} = \frac{1}{N}\sum_{i =1}^{N}{|R_{i,t} - R_{m,t}|},$$

where $R_{i,t}$ observed currency returns from market $i$ at time $t$, $R_{m,t}$ is a trade weighted average of the $R_{i,t}$ or the market return, $w_{i,t}$ is the respective trade weight of each market over time with the South Africa, and the $\sum_{i}w_{i,t}= 1$. The return dispersion measures capture the directional similarity across currency returns at a given point in time with respect to the aggregate market. Herding tests, in turn, are based on the pattern of return dispersions during periods of large price movements. Usually, the return dispersion metrics tend to be positively associated with market returns in the absence of herding. 

<!-- Next, the pattern of return dispersions during periods of large price movements is examined. The rationale behind the testing methodology is that, if herding is present, the correlated trades by investors will lead to greater directional similarity in currency returns, thus leading to lower dispersion in returns. This can be measured by the sign of the coefficients of the relationship between the return dispersion and $R_{m, t}$ and $R_{m, t}^2$ (or market return measures) in these equations for the general market herding: -->

<!-- $$CSSD_{t} = \alpha_0 +  \alpha_1|R_{m, t}| +  \alpha_2R_{m, t}^2 + \epsilon_{t},$$ -->
<!-- $$CSAD_{t} =  \alpha_0 +  \alpha_1|R_{m, t}| +  \alpha_2R_{m, t}^2 + \epsilon_{t},$$ -->

<!-- where $\alpha_2$ is the herding coefficient. The expectation is that $\alpha_1 > 0$ and $\alpha_2=0$, indicating the absence of herding. However, herding would be implied by $\alpha_2 < 0$, which indicates that return dispersions are significantly lower during market stress due to correlated trading behaviour, leading to greater directional similarity in returns. Likewise, $\alpha_2 > 0$ would indicate anti-herding, indicating that traders go against the market consensus [@stavroyiannis2015time]. The purpose of the $CSSD_t$ and the $CSAD_t$ regressions is not to determine the best fit but to test the directional similarity of returns. This is possible because returns data are typically highly correlated and stationary. To ensure that the results are not spurious, all the $CSSD_t$ and the $CSAD_t$ regressions in this study use Heteroskedasticity and Autocorrelation Consistent (HAC) standard errors as defined by @zeileis2004econometric.  -->

# Results

## Descriptive analysis

```{r}
#| label: fig-results-all
#| fig-cap: "Cross sectional deviations."
#| fig-height: 14
#| fig-width: 10
#| cache: true
cross_sectionals <- read_rds(here("Outputs", "artifacts_csad_cssd.rds"))
results_all_gg <- cross_sectionals$graphs$results_all_gg  
results_all_gg
```

## Industry herding in general 


##  Industry herding and economic crises


## Industry herding in the context of political cycles

```{r}
#| label: tbl-political
#| tbl-cap: "Herding and political cycles."
#| cache: true

equation <-  as_equation(c("CSAD_{FUND, t} = \\alpha + \\gamma_1D^{crisis}|R_{m, t}| + \\gamma_2(1-D^{crisis})|R_{m, t}| + \\gamma_3D^{crisis}R_{m, t}^2 +  \\gamma_4(1-D^{crisis})R_{m, t}^2 +  \\epsilon_{t}"))

equation_2 <-  as_equation(c("CSAD_{NONFUND, t} = \\alpha + \\gamma_1D^{crisis}|R_{m, t}| + \\gamma_2(1-D^{crisis})|R_{m, t}| + \\gamma_3D^{crisis}R_{m, t}^2 +  \\gamma_4(1-D^{crisis})R_{m, t}^2 +  \\epsilon_{t}"))
estimates <- c(
  "\\alpha",
  "\\gamma_1 ",
  "\\gamma_2",
  "\\gamma_3 ",
  "\\gamma_4"
)

political <- read_rds(here("Outputs", "artifacts_party_dummy.rds"))
political$ols_party_dummy_model_tbl %>% 
  ungroup() %>% 
  as_grouped_data(groups = c("Group")) %>% 
    as_flextable(hide_grouplabel = TRUE) %>% 
  mk_par(i =, j = 1, part = "header", value = as_paragraph("Industry")) %>% 
  # mk_par(i =, j = c(2, 3, 4, 5, 6), part = "header", value = as_paragraph(as_equation(estimates))) %>% 
  add_footer_row(values = as_paragraph("Note: The numbers in brackets are p-values. A p-value of less than 0.1 is significant", " ", ". The regressions are based on ", equation, " and ", equation_2), colwidths = 4) %>%
  hline_bottom(part = "footer",
               border = fp_border(
                 color = "black",
                 style = "solid",
                 width = 1
               )) %>% 
  align(j = 1, align = "left", part = "all") %>% 
  merge_at(i = 1) %>% 
  align(i = 1, align = "center") %>% 
  merge_at(i = 8) %>% 
  align(i = 8, align = "center") %>% 
  merge_at(i = 15) %>% 
  align(i = 15, align = "center") %>%
  autofit(add_w = 1)
  
```

# Conclusion

\newpage


# References {.unnumbered}
::: {#refs}
:::


\setcounter{section}{0}
\renewcommand{\thesection}{\Alph{section}}

\setcounter{table}{0}
\renewcommand{\thetable}{A\arabic{table}}

\setcounter{figure}{0}
\renewcommand{\thefigure}{A\arabic{figure}}

\newpage

# Appendix: Data

## Industry data

```{r}
#| label: fig-cons
#| fig-cap: "Consumables returns"
#| fig-height: 6
#| fig-width: 6
#| cache: true

returns_data <- read_rds(here("Outputs", "artifacts_returns_data.rds"))
returns_data$graphs$Consumer_durables_nondurables_wholesale_retail_some_services_group_equal_gg
```

```{r}
#| label: fig-health
#| fig-cap: "Health returns"
#| fig-height: 3
#| fig-width: 6
#| cache: true

returns_data$graphs$healthcare_medical_equipment_and_drugs_group_equal_gg
```

```{r}
#| label: fig-manufacturing
#| fig-cap: "Manufacturing returns"
#| fig-height: 6
#| fig-width: 6
#| cache: true

returns_data$graphs$manufacturing_energy_utilities_group_equal_gg
```

```{r}
#| label: fig-business
#| fig-cap: "Business services returns"
#| fig-height: 4
#| fig-width: 6
#| cache: true

returns_data$graphs$business_equipment_telephone_and_television_transmission_group_equal_gg
```

```{r}
#| label: fig-mines
#| fig-cap: "Other returns"
#| fig-height: 8
#| fig-width: 8
#| cache: true

returns_data$graphs$mines_constr_bldmt_trans_hotels_bus_serv_entertainment_finance__group_equal_gg
```
\newpage

## Industry grouping

```{r}
#| label: tbl-grouping
#| tbl-cap: "Industry grouping using CRSP SICs"
#| tbl-colwidths: auto
#| cache: true

aggregation_scheme_tbl <- returns_data$full_data$aggregation_scheme_tbl
aggregation_scheme_tbl %>% 
  flextable() %>% 
  align(align = "left", part = "all") %>% 
  autofit(add_w = -0.1)
```

\newpage

## Crises periods

```{r}
#| label: tbl-crises_description
#| tbl-cap: "Crises periods. Source: Wikipedia (2023)"
#| cache: true

crisis_tbl <- 
  tibble(
  "Crisis" = c("Great Depression", "Dot-com Bubble", "Financial Crisis", "Covid Crisis"),
  "Start" = c("1929-01-01", "1997-01-01", "2007-01-01", "2020-01-01"),
  "End" = c("1939-12-31", "2003-12-31", "2009-12-31", "2021-12-31")
) 

crisis_tbl %>% 
  flextable() %>% 
  align(j = 1, align = "left", part = "all") %>% 
  autofit(add_w = 1.5)

```

\newpage
## Fama-French factors

```{r}
#| label: fig-famafrench
#| fig-cap: "Fama-French Factors"
#| cache: true

famafrench <- read_rds(here("Outputs", "artifacts_fama_french.rds"))
famafrench$graphs$fama_french_gg

```

\newpage
## Presidential terms

```{r}
#| label: tbl-terms
#| tbl-cap: "Presidential terms"
#| cache: true

# importing presidential terms
presidential_terms <- read_rds(here("Outputs", "artifacts_presidential_terms.rds"))
presential_terms_tbl <- 
  presidential_terms$terms_tbl %>% 
  filter(Term_start >= "1920-01-01") %>%
  rename(
    "Start" = "Term_start",
    "End" = "Term_end") %>% 
  mutate(
    "Start" = lubridate::year(Start),
    "End" = lubridate::year(End)
  )

# creating table of presidential terms
presential_terms_tbl %>% 
  flextable() %>% 
  align(j = 1, align = "left", part = "all") %>% 
  colformat_double(j = 2:3, digits = 0, big.mark = "") %>%
  autofit(add_w = 2)

```

\newpage

\setcounter{table}{0}
\renewcommand{\thetable}{B\arabic{table}}

\setcounter{figure}{0}
\renewcommand{\thefigure}{B\arabic{figure}}

#  Appendix: Industry herding results

## Descriptive statistics

```{r}
#| label: tbl-desc
#| tbl-cap: "Descriptive statistics"
#| cache: true

descriptives <- read_rds(here("Outputs", "artifacts_descriptives.rds"))
descriptives_tbl <- 
  descriptives$descriptives_tbl %>% 
  ungroup()


descriptives_tbl %>%
  as_grouped_data(groups = c("Category")) %>%
  as_flextable(hide_grouplabel = TRUE) %>% 
  align(align = "center", part = "all") %>% 
  align(align = "left", j = 1, part = "all") %>% 
  align(align = "left", j = 2, part = "all") %>% 
  merge_at(i = 1) %>% 
  align(i = 1, align = "center") %>% 
  merge_at(i = 12) %>%
  align(i = 12, align = "center") %>%
  merge_at(i = 23) %>%
  align(i = 23, align = "center") %>%
  merge_at(i = 34) %>% 
  align(i = 34, align = "center") %>%
  merge_at(i = 45) %>%
  align(i = 45, align = "center") %>%
  merge_at(i = 56) %>%
  align(i = 56, align = "center") %>%
  autofit(add_w = 0.45)

```
 
\newpage
##  General industry herding

```{r}
#| label: tbl-ols
#| tbl-cap: "Industry herding ols results"
#| cache: true

equation <-  as_equation(c("CSAD_{t} = \\alpha + \\gamma_1|R_{m, t}| +  \\gamma_2R_{m, t}^2 +  \\epsilon_{t}"))
estimates <- c(
  "\\alpha",
  "\\gamma_1 ",
  "\\gamma_2"
)

general_herding <- read_rds(here("Outputs", "artifacts_general_herding.rds"))
general_herding$models$ols_combined_tbl %>% 
 ungroup() %>% 
 as_grouped_data(groups = c("Extreme")) %>%
 as_flextable(hide_grouplabel = TRUE) %>%
  mk_par(i =, j = 1, part = "header", value = as_paragraph("Industry")) %>% 
  mk_par(i =, j = c(2, 3, 4), part = "header", value = as_paragraph(as_equation(estimates))) %>% 
    add_footer_row(values = as_paragraph("Note: The numbers in brackets are p-values. A p-value of less than 0.1 is significant", " ", ". The regressions are based on ", equation), colwidths = 4) %>% 
  hline_bottom(part = "footer", border = fp_border(color = "black", style = "solid", width = 1)) %>% 
  align(j = 1, align = "left", part = "all") %>% 
  merge_at(i = 1) %>% 
  align(i = 1, align = "center") %>% 
  merge_at(i = 8) %>% 
  align(i = 8, align = "center") %>% 
  merge_at(i = 15) %>% 
  align(i = 15, align = "center") %>% 
  autofit(add_w = 0.7)

```

```{r}
#| label: fig-rol_gen
#| fig-cap: "Industry herding rolling regressions with 250 day window. Note: The perforated lines represents a 5% level of significance."
#| fig-height: 6
#| fig-width: 8
#| cache: true


CSAD_model_rol_gg <- general_herding$graphs$rol_gg
CSAD_model_rol_gg
```

\newpage

## Industry herding in crisis periods


```{r}
#| label: tbl-ols_crisis
#| tbl-cap: "Industry herding in crisis periods"
#| cache: true
#| include: true
#| eval: true

equation <-  as_equation(c("CSAD_{t} = \\alpha + \\gamma_1D^{crisis}|R_{m, t}| + \\gamma_2(1-D^{crisis})|R_{m, t}| + \\gamma_3D^{crisis}R_{m, t}^2 +  \\gamma_4(1-D^{crisis})R_{m, t}^2 +  \\epsilon_{t}"))
estimates <- c(
  "\\alpha",
  "\\gamma_1 ",
  "\\gamma_2",
  "\\gamma_3 ",
  "\\gamma_4"
)

CSAD_model_rol_crisis <- read_rds(here("Outputs", "artifacts_herding_crisis.rds"))
CSAD_model_rol_crisis_tbl <- CSAD_model_rol_crisis$models$combined_regression_tbl


CSAD_model_rol_crisis_tbl %>%
    ungroup() %>% 
  as_grouped_data(groups = c("Crisis")) %>% 
    as_flextable(hide_grouplabel = TRUE) %>%  
   mk_par(i =, j = 1, part = "header", value = as_paragraph("Industry")) %>% 
   mk_par(i =, j = c(2, 3, 4, 5, 6), part = "header", value = as_paragraph(as_equation(estimates))) %>% 
    add_footer_row(values = as_paragraph("Note: The numbers in brackets are p-values. A p-value of less than 0.1 is significant", " ", ". The regressions are based on ", equation), colwidths = 6) %>% 
  hline_bottom(part = "footer", border = fp_border(color = "black", style = "solid", width = 1)) %>% 
  align(j = 1, align = "left", part = "all") %>% 
  merge_at(i = 1) %>% 
  align(i = 1, align = "center") %>% 
  merge_at(i = 8) %>% 
  align(i = 8, align = "center") %>% 
  merge_at(i = 15) %>% 
  align(i = 15, align = "center") %>% 
  merge_at(i = 22) %>% 
  align(i = 22, align = "center") %>% 
  autofit(add_w = 0.1)


```

```{r}
#| label: fig-rol_crisis_gd
#| fig-cap: "Industry herding during the Great Depression using a 250-day rolling window. Note: The perforated lines represents a 5% level of significance."
#| fig-height: 6
#| fig-width: 8
#| cache: true

CSAD_model_rol_crisis$graphs$rol_gd_gg


```

```{r}
#| label: fig-rol_crisis_db
#| fig-cap: "Industry herding during the Dot-com Bubble using a 250-day rolling window. Note: The perforated lines represents a 5% level of significance."
#| fig-height: 6
#| fig-width: 8
#| cache: true

CSAD_model_rol_crisis$graphs$rol_db_gg
```

```{r}
#| label: fig-rol_crisis_fc
#| fig-cap: "Industry herding during the Financial Crisis using a 250-day rolling window. Note: The perforated lines represents a 5% level of significance."
#| fig-height: 6
#| fig-width: 8
#| cache: true

CSAD_model_rol_crisis$graphs$rol_fc_gg
```

```{r}
#| label: fig-rol_crisis_cv
#| fig-cap: "Industry herding during the Covid Crisis using a 250-day rolling window. Note: The perforated lines represents a 5% level of significance."
#| fig-height: 6
#| fig-width: 8
#| cache: true

CSAD_model_rol_crisis$graphs$rol_cv_gg
```

\newpage

## Industry herding on fundamental information

```{r}
#| label: tbl-ols_fund
#| tbl-cap: "Industry herding on fundamental information"
#| cache: true
#| include: true
#| eval: true

equation <-  as_equation(c("CSAD_{t} = \\alpha + \\gamma_1R_{m, t}| + \\gamma_2R_{m, t}^2 + \\epsilon_{t}"))
estimates <- c(
  "\\alpha",
  "\\gamma_1 ",
  "\\gamma_2"
)

CSAD_model_fundmamental <- read_rds(here("Outputs", "artifacts_fundamental_herding.rds"))
CSAD_model_fundamental_tbl <- CSAD_model_fundmamental$ols$ols_fund_tbl


CSAD_model_fundamental_tbl %>%
    ungroup() %>% 
  as_grouped_data(groups = c("Herd")) %>% 
    as_flextable(hide_grouplabel = TRUE) %>% 
   mk_par(i =, j = 1, part = "header", value = as_paragraph("Industry")) %>% 
   mk_par(i =, j = c(2, 3, 4), part = "header", value = as_paragraph(as_equation(estimates))) %>% 
    add_footer_row(values = as_paragraph("Note: The numbers in brackets are p-values. A p-value of less than 0.1 is significant", " ", ". The regressions are based on ", equation), colwidths = 4) %>% 
  hline_bottom(part = "footer", border = fp_border(color = "black", style = "solid", width = 1)) %>% 
  align(j = 1, align = "left", part = "all") %>% 
  merge_at(i = 1) %>% 
  align(i = 1, align = "center") %>% 
  merge_at(i = 8) %>% 
  align(i = 8, align = "center") %>% 
  autofit(add_w = 0.6)


```


```{r}
#| label: fig-rol_fundamental
#| fig-cap: "Industry herding on fundamental information using a 250-day rolling window. Note: The perforated lines represents a 5% level of significance."
#| fig-height: 6
#| fig-width: 8
#| cache: true

CSAD_model_fundmamental$ols_rol_graphs$rol_fundamental_gg

```


```{r}
#| label: fig-rol_nonfundamental
#| fig-cap: "Industry herding on non-fundamental information using a 250-day rolling window. Note: The perforated lines represents a 5% level of significance."
#| fig-height: 6
#| fig-width: 8
#| cache: true

CSAD_model_fundmamental$ols_rol_graphs$rol_nonfundamental_gg

```

\newpage
## Industry herding on fundamental information in crisis periods

```{r}
#| label: tbl-ols_crisis_fund
#| tbl-cap: "Industry herding on fundamental information in crisis periods"
#| cache: true
#| include: true
#| eval: true

equation <-  as_equation(c("CSAD_{FUND, t} = \\alpha + \\gamma_1D^{crisis}|R_{m, t}| + \\gamma_2(1-D^{crisis})|R_{m, t}| + \\gamma_3D^{crisis}R_{m, t}^2 +  \\gamma_4(1-D^{crisis})R_{m, t}^2 +  \\epsilon_{t}"))

equation_2 <-  as_equation(c("CSAD_{NONFUND, t} = \\alpha + \\gamma_1D^{crisis}|R_{m, t}| + \\gamma_2(1-D^{crisis})|R_{m, t}| + \\gamma_3D^{crisis}R_{m, t}^2 +  \\gamma_4(1-D^{crisis})R_{m, t}^2 +  \\epsilon_{t}"))
estimates <- c(
  "\\alpha",
  "\\gamma_1 ",
  "\\gamma_2",
  "\\gamma_3 ",
  "\\gamma_4"
)

CSAD_model_rol_crisis_fund <- read_rds(here("Outputs", "artifacts_crisis_fundamental.rds"))
CSAD_model_rol_crisis_fund_tbl <- CSAD_model_rol_crisis_fund$ols$ols_tbl


CSAD_model_rol_crisis_fund_tbl %>%
    ungroup() %>% 
  as_grouped_data(groups = c("Fund")) %>% 
    as_flextable(hide_grouplabel = TRUE) %>%  
   mk_par(i =, j = 1, part = "header", value = as_paragraph("Industry")) %>% 
   mk_par(i =, j = c(2, 3, 4, 5, 6), part = "header", value = as_paragraph(as_equation(estimates))) %>% 
    add_footer_row(values = as_paragraph("Note: The numbers in brackets are p-values. A p-value of less than 0.1 is significant", " ", ". The regressions are based on ", equation, " and ", equation_2), colwidths = 6) %>% 
  hline_bottom(part = "footer", border = fp_border(color = "black", style = "solid", width = 1)) %>% 
  align(j = 1, align = "left", part = "all") %>% 
  merge_at(i = 1) %>% 
  align(i = 1, align = "center") %>% 
  merge_at(i = 8) %>% 
  align(i = 8, align = "center") %>% 
  merge_at(i = 15) %>% 
  align(i = 15, align = "center") %>% 
  merge_at(i = 22) %>% 
  align(i = 22, align = "center") %>% 
  merge_at(i = 29) %>% 
  align(i = 29, align = "center") %>% 
  merge_at(i = 36) %>% 
  align(i = 36, align = "center") %>% 
  merge_at(i = 43) %>% 
  align(i = 43, align = "center") %>% 
  merge_at(i = 50) %>% 
  align(i = 50, align = "center") %>% 
  autofit(add_w = 0.1)


```



```{r}
#| label: fig-rol_fundamental_gd
#| fig-cap: "Industry herding on fundamental information during the Great depression using a 250-day rolling window. Note: The perforated lines represents a 5% level of significance."
#| fig-height: 6
#| fig-width: 8
#| cache: true

crisis_fundamental <- read_rds(here("Outputs", "artifacts_crisis_fundamental.rds"))

crisis_fundamental$fundamental$rol_fund_gd_gg
```


```{r}
#| label: fig-rol_fundamental_db
#| fig-cap: "Industry herding on fundamental information during the Dot-com bubble using a 250-day rolling window. Note: The perforated lines represents a 5% level of significance."
#| fig-height: 6
#| fig-width: 8
#| cache: true

crisis_fundamental$fundamental$rol_fund_db_gg
```


```{r}
#| label: fig-rol_fundamental_fc
#| fig-cap: "Industry herding on fundamental information during the Financial crisis using a 250-day rolling window. Note: The perforated lines represents a 5% level of significance."
#| fig-height: 6
#| fig-width: 8
#| cache: true

crisis_fundamental$fundamental$rol_fund_fc_gg
```


```{r}
#| label: fig-rol_fundamental_cv
#| fig-cap: "Industry herding on fundamental information during the Covid crisis using a 250-day rolling window. Note: The perforated lines represents a 5% level of significance."
#| fig-height: 6
#| fig-width: 8
#| cache: true

crisis_fundamental$fundamental$rol_fund_cv_gg
```


```{r}
#| label: fig-rol_nonfundamental_gd
#| fig-cap: "Industry herding on non-fundamental information during the Great depression using a 250-day rolling window. Note: The perforated lines represents a 5% level of significance."
#| fig-height: 6
#| fig-width: 8
#| cache: true

crisis_fundamental$nonfundamental$rol_nonfund_gd_gg
```


```{r}
#| label: fig-rol_nonfundamental_db
#| fig-cap: "Industry herding on non-fundamental information during the Dot-com bubble using a 250-day rolling window. Note: The perforated lines represents a 5% level of significance."
#| fig-height: 6
#| fig-width: 8
#| cache: true

crisis_fundamental$nonfundamental$rol_nonfund_db_gg
```


```{r}
#| label: fig-rol_nonfundamental_fc
#| fig-cap: "Industry herding on non-fundamental information during the Financial crisis using a 250-day rolling window. Note: The perforated lines represents a 5% level of significance."
#| fig-height: 6
#| fig-width: 8
#| cache: true

crisis_fundamental$nonfundamental$rol_nonfund_fc_gg
```


```{r}
#| label: fig-rol_nonfundamental_cv
#| fig-cap: "Industry herding on non-fundamental information during the Covid crisis using a 250-day rolling window. Note: The perforated lines represents a 5% level of significance."
#| fig-height: 6
#| fig-width: 8
#| cache: true

crisis_fundamental$nonfundamental$rol_nonfund_cv_gg
```

\newpage



# References
