---
format:
  pdf:
    tbl-cap-location: top
    dpi: 500
    fig-pos: "H"
    number-sections: true
    cite-method: natbib
    include-in-header: preamble.tex
    include-before-body: title.tex
pdf-engine: lualatex
monofont: "DejaVu Sans Mono"
mainfont: "Times New Roman"
execute: 
  echo: false
  warning: false
editor: source
bibliography: references.bib
biblio-style: apalike
natbiboptions: round
link-citations: true
linkcolor: blue!000!black
urlcolor: blue!000!black
citecolor: blue!000!black
linestretch: 1.5
indent: TRUE
---

```{r}
#| label: setup
#| include: false
options(scipen=999)
knitr::opts_chunk$set(
                      fig.pos = "H", 
                      fig.env= 'figure', 
                      ft.align = "left",
                      ft.tabcolsep= 0, 
                      ft.latex.float = "none",
                      ft.arraystretch = 0.4
                      )
library(tidyverse)
library(readr)
library(readxl)
library(zoo)
library(magick)
library(stringi)
library(patchwork)
library(xtable)
library(scales)
library(rvest)
library(rebus)
library(PNWColors)
library(lubridate)
library(here)
library(flextable)
library(gt)
library(officer)
library(officedown)
library(modelsummary)
library(sandwich)
library(lmtest)
library(stargazer)
```

```{r}
#| label: func
source(here("Functions","flextable_word.R" ))
source(here("Functions","modelsummary_pdf.R" ))
source(here("Functions","borderlines.R" ))

set_flextable_defaults(font.size = 7, 
                       text.align = "left", 
                       font.color = "black", 
                       theme_fun = theme_apa, 
                       padding = 0,
                       line_spacing = 0)
```


# Introduction

@duygun2021


# Literature Review

## Introduction
* Provide an overview of the concept of herding behavior in the context of financial markets.

Herding behavior in financial markets is a significant and pervasive phenomenon, leading to informational inefficiencies and driving asset prices away from their fundamental value (Cipriani, 2010). It is a key concern due to its potential to increase market volatility, destabilize the market, and make it more fragile (Dewan, 2019). This behavior is often influenced by external factors such as market conditions, volatility, and liquidity (Dewan, 2019). The presence of herd behavior in the Chinese stock market has been confirmed, with investors being particularly susceptible to it (Zhang, 2016). The efficiency of herd behavior is closely linked to the market's ability to absorb new information (Tian-rong, 2005).

@Tianrong2005HerdBI
@Zhang2016ASO
@Dewan2019HerdingBI
@Cipriani2010EstimatingAS

* Introduce the specific focus on industry-level herding behavior.

Industry herding is a significant phenomenon in the stock market, with implications for both individual and institutional investors. Ganesh (2016) found that industry herding can influence stock market behavior, while Demirer (2019) and Yan (2012) both highlighted the potential for enhanced momentum profits through the use of industry herding. Camara (2017) further explored the impact of industry herding on financing decision making, identifying significant evidence of herding in specific industries during different market conditions. These studies collectively underscore the importance of industry herding in shaping market dynamics and investment strategies.

@Ganesh2016IndustryHB
@Demirer2019IndustryHA
@camara2017industry


* State the importance of understanding industry herding behavior for investors, policymakers, and academics.

Understanding industry herding behavior is crucial for investors, policymakers, and academics due to its potential impact on market stability and efficiency. Ganesh (2016) found that industry herding behavior was not a significant factor in the Indian stock market, while Zhang (2016) identified clear evidence of herding in the Chinese stock market. Dewan (2019) provided a comprehensive review of herding behavior, including its types, significance, and determinants, and highlighted the need for further research in this area. Jiang (2018) explored the role of platform attributes and regulations in moderating herding behavior in the context of online peer-to-peer lending, suggesting that these factors can influence the magnitude of the herding effect. These studies collectively underscore the importance of understanding industry herding behavior for various stakeholders, as it can have significant implications for investment decision-making, market stability, and regulatory interventions.

@Ganesh2016IndustryHB
@Dewan2019HerdingBI
@Zhang2016ASO

* Outline the objectives and structure of the literature review.

## Theoretical Framework
* Discuss the theoretical foundations of herding behavior, drawing from behavioral finance, information cascades, and related theories.
* Explain how these theories apply to industry-level dynamics and how they shape herding behavior among investors and market participants.

Theoretical foundations of herding behavior, as discussed by Hirshleifer (2001, 2003, 2008) and Zhang (2016), draw from behavioral finance, information cascades, and related theories. These theories explain how industry-level dynamics are shaped by herding behavior among investors and market participants. Behavioral finance, for instance, incorporates psychology and sociology to understand how investors handle information and make decisions. Information cascades theory, on the other hand, explores how individuals follow the actions of others, leading to herding behavior. These theories are particularly relevant in the Chinese stock market, where Zhang (2016) found evidence of herd behavior among institutional investors.

@boortz2013herding
@Spyrou2013HerdingIF
@Hirshleifer2003HerdBA


## Empirical Evidence on Industry Herding
* Review empirical studies that have examined industry herding behavior.
* Organize the review chronologically or thematically, depending on the literature.
* Summarize key findings regarding the prevalence, determinants, and consequences of industry herding.
* Highlight any inconsistencies or gaps in the literature.

Empirical studies have consistently found that industry herding behavior is more pronounced in down markets, with investors tending to herd more during bearish periods (Bouzid, 2020; Zheng, 2017; Zheng, 2016). This behavior is particularly strong in the Technology and Financial industries, and weaker in the Utility industry (Zheng, 2017; Zheng, 2016). However, the Fast Moving Consumer Goods (FMCG) sector, which is non-cyclical, does not display herding behavior, possibly due to investors relying more on fundamentals (Bharti, 2020). The presence of industry herding is also influenced by market conditions, with it being more pronounced in low trading volume markets (Zheng, 2017; Zheng, 2016).

@Babalos2015DoCI
@Demirer2019IndustryHA
@shrotryia2021analysis
@Liu2014HerdingBI
@cakan2016sectoral
@Yan2012IndustryHA
@Lee2013IndustryHA
@Choi2008InstitutionalIH
@Camara2017IndustryHB
@zheng2017herding
@bharti2020herding
@bouzid2020industry
@zhao2022industry

### Determinants of Industry Herding
* Discuss factors that influence industry herding behavior, including market conditions, investor characteristics, and information environment.
* Explore the role of institutional investors, market sentiment, and industry-specific factors in driving herding tendencies.
* Analyze how macroeconomic variables, regulatory changes, and technological advancements impact industry-level herding behavior.

Research on the determinants of industry herding behavior has yielded mixed results. Ukpong (2021) found that herding is more prevalent at the industry level, with significant evidence of anti-herding behavior. This is further supported by Ukpong (2019), who identified low trading volatility and volume as key factors in industry herding, particularly during market crises. Camara (2017) and Zheng (2017) both found evidence of industry herding, with Camara highlighting the role of economic conditions and industry-specific factors, and Zheng noting the influence of market conditions and industry characteristics. These studies collectively suggest that industry herding behavior is influenced by a complex interplay of market and industry-specific factors.

@madaan2023determinants
@ukpong2021determinants
@allam2020determinants



## Consequences of Industry Herding
* Examine the consequences of industry herding for market efficiency, volatility, and stability.
* Discuss the implications of industry herding for asset pricing, market liquidity, and systemic risk.
* Consider the effects of herding on industry competition, corporate decision-making, and resource allocation.

Industry herding, particularly by hedge funds, can lead to long-term return reversals and a failure to react to good news (Çaglayan, 2019, 2021). However, it can also impact the performance of winner and loser industries, with a potential for enhanced momentum profits (Demirer, 2019). The interaction between herding and momentum can magnify the momentum effect, with low levels of herding potentially enhancing market efficiency (Yan, 2012).


## Methodological Approaches
* Review the methodologies used to measure and analyze industry herding behavior.
* Compare different approaches, such as statistical tests, modeling techniques, and data sources.
* Evaluate the strengths and limitations of existing methodologies and suggest potential improvements.

A range of methodological approaches have been used in industry herding studies. Frey (2012) proposed a structural approach to measure mutual fund herding, which was found to be unbiased and statistically superior. Mand (2020) and Mand (2021) both demonstrated the effectiveness of a dynamic regime-sensitive approach in uncovering herding behavior, particularly in the financial sector and large- and mid-capitalization segments. These studies collectively highlight the importance of methodological rigor and the potential for dynamic models to provide deeper insights into herding behavior.

@frey2014measuring
@mand2021static

## Future Directions and Research Challenges
* Identify gaps in the literature and areas for future research on industry herding behavior.
* Propose theoretical extensions, empirical investigations, and methodological advancements.
* Discuss the challenges and limitations of studying industry herding and suggest strategies to overcome them.

Herding behavior, where individuals act collectively without centralized direction, is a significant factor in financial markets, driving asset prices away from their fundamental value and potentially destabilizing the market (Dewan, 2019). This behavior is particularly pronounced in the Technology and Financial industries in Asian markets, especially during down markets and low trading volume periods (Zheng, 2017). However, the Indian stock market does not appear to be influenced by industry herding behavior (Ganesh, 2016). Despite the extensive research on herding behavior, there are still open issues and areas with inconclusive evidence, particularly in markets other than equity markets (Spyrou, 2013). Future research should focus on addressing these gaps and limitations.

## Conclusion
* Summarize the key findings and insights from the literature review.
* Reiterate the significance of understanding industry herding behavior.
* Offer concluding remarks on the state of the literature and opportunities for further research.

#  Data and Methodology

## Data

Our analysis utilises Kenneth French's 49 industry portfolio returns.^[\url{http://mba.tuck.dartmouth.edu/pages/faculty/ken.french}] Through his website Kenneth French provides a variety of financial market related data for research purposes, which include the famous Fama/French factors data. These data have two main advantages for researchers. First, the industry portfolio data varies in detail from 5 to 49 industry data-sets. Second, the data cover long periods of time, typically to pre World War II. Specifically, the daily data covers the period 1 July 1926 to 29 July 2022. The significant length and breadth of this data is essential for our analysis.   

We create 5 industry groups from the 49 industries in order to calculate the cross sectional dispersions as outlined in the methodology. In the data, stocks are assigned from the NYSE, AMEX, NASDAQ to an industry portfolio using a four-digit Centre for Research in Security Prices Standard Industry Classification Codes (CSRP-SIC).^[At the end of June each year] Essentially, the CSRP-SICs determine the level of industry aggregation in the data. Therefore, in @tbl-grouping we group the industries using the CSRP-SICs.^[These are also available from \url{http://mba.tuck.dartmouth.edu/pages/faculty/ken.french}] Lastly, @fig-cons to @fig-mines, and @tbl-desc show the described industry data. 

In addition, we focus on herding behaviour in periods of financial crisis. Therefore, we use Wikipedia  to identify 5 crises periods.^[\url{https://en.wikipedia.org/wiki/List_of_economic_crises}] That is, the Great Depression, Dot-com Bubble, Great Financial Crisis and the recent Covid-Crisis. The crises periods are shown in @tbl-crises_description. 

Lastly, in order to understand the effect of political cycles on industry herding we estimate the relationship between the time-varying herding coefficient and US presidential terms as outlined in @eq-political below.^[The US presidential terms can be found at \url{https://en.wikipedia.org/wiki/List_of_United_States_presidential_election_dates}] The US presidential terms are shown in @tbl-terms. In order to match with the industry herding coefficients, the terms  are converted to a daily frequency.

## Testing for industry herding 

Following @christie1995following and @chang2000examination we calculate the  cross-sectional absolute standard deviations ($CSAD_{t}$) for each industry group. The $CSAD_{t}$ is calculated for all markets as follows:

$$CSAD_{t} = \frac{1}{N}\sum_{i =1}^{N}{|R_{i,t} - R_{m,t}|},$$ {#eq-csad}

where $R_{i,t}$ observed returns from individual industry $i$ at time $t$, $R_{m,t}$ is the average of the $R_{i,t}$ or the market return. In this case, $R_{m,t}$ is the group industry return which is an average of the individual industry returns. The return dispersion measures capture the directional similarity industry returns at a given point in time with respect to the aggregate market or group return. Herding tests, in turn, are based on the pattern of return dispersions during periods of large price movements. 

The rationale behind the testing methodology is that, if herding is present, the correlated trades by investors will lead to greater directional similarity in industry returns, thus leading to lower dispersion in returns. This can be measured by the sign of the coefficients of the relationship between the return dispersion and $R_{m, t}$ and $R_{m, t}^2$ (or market return measures) in these equations for the general market herding:


$$CSAD_{t} = \gamma_0 +  \gamma_1|R_{m, t}| +  \gamma_2R_{m, t}^2 + \epsilon_{t},$$ {#eq-csad2}

where $\gamma_2$ is the herding coefficient. The expectation is that $\gamma_1 > 0$ and $\gamma_2 < 0$ if herding is present. $R_{m, t}^2$, therefore, is a non-linear term which captures the herding effect. This non-linear effect implies no herding when $\gamma_2 = 0$, anti-herding when $\gamma_2 > 0$ and, obviously, herding when $\gamma_2 < 0$. We estimate $CSAD_{t}$ with heteroskedastic and autocorrelation consistent (HAC) standard errors [See @newey1987simple].^[We utilise the Newey-West estimator for all estimations in this paper.] Furthermore, for all testing equations, we estimate changes in herding behaviour over time using a rolling-window approach with a 250 day.^[This is a commonly used window in the literature. We do this throughout the herding analysis]  
 

##  Industry herding in periods of financial crisis

Herding is known to be more pronounced in times of market crisis. To test for this we use a dummy variable approach to test whether herding is more pronounced during periods of financial crisis. @eq-csad2 is adjusted to include the $D^{crisis}$, which is an crisis period indicator, as follows:

$$
\begin{aligned}
CSAD_{t} = \gamma_0 +  \gamma_1D^{crisis}|R_{m, t}| + \gamma_2(1 - D^{crisis})|R_{m,t}| + \\  \gamma_3D^{crisis}R_{m, t}^2 + \gamma_4(1-D^{crisis})R_{m,t}^2 + \epsilon_{t},
\end{aligned}
$$ {#eq-csad3}

where $D_{crisis}$ is a dummy variable which takes the value of 1 during periods of financial crisis and 0 otherwise. That is, to isolate the herding effect ($\gamma_3D^{crisis}R_{m, t}^2$) only to periods of market crisis. Therefore,  in @eq-csad3 herding is present if $\gamma_3 < 0$ and is significant. 

## Industry herding and fundamental information
Herding can be considered either a rational response to public information by investors, or an accumulation of irrational behaviour by investors due to, for example, fear of under performance or fear of missing out on a market run [see @Bikhchandani2001]. In order to test for the rationality of herding, we test whether herding is related to fundamental information. We use the following equations to test for the relationship between herding and fundamental information, and herding and non-fundamental information. First we isolate the non-fundamental component of herding as follows:

$$CSAD_t = \alpha + \beta_1(R_{m,t} - Rf_t) + \beta_2HML_t + \beta_3SMB_t + \xi_t,$${#eq-info}

where $Rf_t$ is the risk-free rate, $HML_t$ is the high-minus-low portfolio and $SMB_t$ is the small-minus-big portfolio. The $Rf_t$, $HML_t$ and $SMB_t$ are all from the Fama-French 3 factor model [see @fama1993common] and are shown in @fig-famafrench. 

The non-fundamental component of herding is then:
$$CSAD_{NONFUND, t} = \xi_t. $${#eq-nonfunda}

It stands to reason that the fundamental component of herding is then:
$$CSAD_{FUND, t} = CSAD_t - CSAD_{NONFUND, t},$${#eq-funda}

where $CSAD_{FUND, t}$ is the fundamental component of herding. 

We then test the relationship between $CSAD_{NONFUND, t}$ and $CSAD_{FUND, t}$ and herding  as follows:

$$CSAD_{NONFUND,t} = \gamma_0 +  \gamma_1|R_{m, t}| +  \gamma_2R_{m, t}^2 + \epsilon_{t},$$ {#eq-nonfundaherd}

$$CSAD_{FUND,t} = \gamma_0 +  \gamma_1|R_{m, t}| +  \gamma_2R_{m, t}^2 + \epsilon_{t},$$ {#eq-fundaherd}

where $\gamma_2$ is the herding coefficient. Again, the expectation is that $\gamma_1 > 0$ and $\gamma_2 < 0$ if herding is present.

Extending the analysis further, we test if the rational and irrational components of herding are more pronounced during periods of financial crisis. We use the following equations to test for the relationship between herding and fundamental information, and herding and non-fundamental information during periods of financial crisis:

$$
\begin{aligned}
CSAD_{NONFUND, t} = \gamma_0 +  \gamma_1D^{crisis}|R_{m, t}| + \gamma_2(1 - D^{crisis})|R_{m,t}|  + \\  
\gamma_3D^{crisis}R_{m, t}^2 + \gamma_4(1-D^{crisis})R_{m,t}^2 + \epsilon_{t},
\end{aligned}
$$ {#eq-nonfundacrisis}

$$
\begin{aligned}
CSAD_{FUND, t} = \gamma_0 +  \gamma_1D^{crisis}|R_{m, t}| + \gamma_2(1 - D^{crisis})|R_{m,t}|  + \\ \gamma_3D^{crisis}R_{m, t}^2 + \gamma_4(1-D^{crisis})R_{m,t}^2 + \epsilon_{t},
\end{aligned}
$$ {#eq-fundacrisis}

where, again, to isolate the herding effect ($\gamma_3D^{crisis}R_{m, t}^2$) to periods of market crisis. $D_{crisis}$ is a dummy variable which takes the value of 1 during periods of financial crisis and 0 otherwise. Therefore, both in  @eq-nonfundacrisis and @eq-fundacrisis herding is present if $\gamma_3 < 0$ and is significant.

## Industry herding and political cycles
 
Inspired by the resent findings that risk aversion is a determinant of herding [@nath2020investor], we construct a somewhat novel test to ask whether herding is related to political cycles. After taking market volatility into account, we estimate the following equations:

$$Pr(D^{herd} = 1 |\lambda_0 +  \lambda_1D^{party}  + \lambda_2\Gamma_t) = \lambda_0 +  \lambda_1D^{party}  + \lambda_2\Gamma_t,$$ {#eq-political}

where $D^{herd}$ is dummy variable with value 1 when herding is present and 0 otherwise. $D^{party}$ is a dummy variable which takes the value of 1 for the Democratic party, and 0 for the Republican party.^[@eq-political, @eq-politicalnonfund and @eq-politicalfund were estimated as linear probability and probit models. The estimates of the linear probability model are the similar to the probit marginal effects. For simplicity we use the linear probability model estimates. The probit marginal effects are shown in @tbl-probit] $\lambda_0$ is the Republican party estimate. $\Gamma_t$ is the market volatility from a $GARCH(1,1)$ model of the overall market returns (CSRP) of the industry portfolios as described above, and is shown in @fig-volatility. 

A natural question which follows is if the political cycle is a determinant herding, how is this affected by the rational or irrational herding. A similar analysis is conducted using herding related to fundamental and non-fundamental information in the following manner:

$$
Pr(D^{herd}_{NONFUND} = 1 |\lambda_0 +  \lambda_1D^{party}  + \lambda_2\Gamma_t) = \lambda_0 +  \lambda_1D^{party}  + \lambda_2\Gamma_t,
$$ {#eq-politicalnonfund}

$$Pr(D^{herd}_{FUND}= 1 |\lambda_0 +  \lambda_1D^{party}  + \lambda_2\Gamma_t) = \lambda_0 +  \lambda_1D^{party}  + \lambda_2\Gamma_t,$$ {#eq-politicalfund}

where $D^{herd}_{NONFUND}$ and $D^{herd}_{FUND}$ are dummy variables with value 1 when non-fundamental and fundamental herding is present and 0 otherwise. 



# Results

## Descriptive analysis

\newpage
```{r}
#| label: tbl-desc
#| tbl-cap: "Descriptive statistics"
#| cache: true

descriptives <- read_rds(here("Outputs", "artifacts_descriptives.rds"))
descriptives_tbl <- 
  descriptives$descriptives_tbl %>% 
  ungroup()


descriptives_tbl %>%
  as_grouped_data(groups = c("Category")) %>%
  as_flextable(hide_grouplabel = TRUE) %>% 
  align(align = "center", part = "all") %>% 
  align(align = "left", j = 1, part = "all") %>% 
  align(align = "left", j = 2, part = "all") %>% 
  merge_at(i = 1) %>% 
  align(i = 1, align = "center") %>% 
  merge_at(i = 12) %>%
  align(i = 12, align = "center") %>%
  merge_at(i = 23) %>%
  align(i = 23, align = "center") %>%
  merge_at(i = 34) %>% 
  align(i = 34, align = "center") %>%
  merge_at(i = 45) %>%
  align(i = 45, align = "center") %>%
  merge_at(i = 56) %>%
  align(i = 56, align = "center") %>%
  autofit(add_w = 0.45)

```
 

```{r}
#| label: fig-results-all
#| fig-cap: "Cross sectional deviations."
#| fig-height: 14
#| fig-width: 10
#| cache: true
#| include: false
#| eval: false

cross_sectionals <- read_rds(here("Outputs", "artifacts_csad_cssd.rds"))
results_all_gg <- cross_sectionals$graphs$results_all_gg  
results_all_gg
```

\newpage
## Evidence of industry herding in the US 

```{r}
#| label: tbl-ols
#| tbl-cap: "Industry herding ols results"
#| cache: true

equation <-  as_equation(c("CSAD_{t} = \\gamma + \\gamma_1|R_{m, t}| +  \\gamma_2R_{m, t}^2 +  \\epsilon_{t}"))
estimates <- c(
  "\\gamma",
  "\\gamma_1 ",
  "\\gamma_2"
)

general_herding <- read_rds(here("Outputs", "artifacts_general_herding.rds"))
general_herding$models$ols_combined_tbl %>% 
 ungroup() %>% 
 as_grouped_data(groups = c("Extreme")) %>%
 as_flextable(hide_grouplabel = TRUE) %>%
  mk_par(i =, j = 1, part = "header", value = as_paragraph("Industry")) %>% 
  mk_par(i =, j = c(2, 3, 4), part = "header", value = as_paragraph(as_equation(estimates))) %>% 
    add_footer_row(values = as_paragraph("Note: *** = p value < 0.01, ** = 0.01 < p value < 0.05, * = 0.05 < p value < 0.1.", " ", " The regressions are based on ", equation), colwidths = 4) %>% 
  hline_bottom(part = "footer", border = fp_border(color = "black", style = "solid", width = 1)) %>% 
  align(j = 1, align = "left", part = "all") %>% 
  merge_at(i = 1) %>% 
  align(i = 1, align = "center") %>% 
  merge_at(i = 8) %>% 
  align(i = 8, align = "center") %>% 
  merge_at(i = 15) %>% 
  align(i = 15, align = "center") %>% 
  autofit(add_w = 0.7)

```

```{r}
#| label: fig-rol_gen
#| fig-cap: "Industry herding rolling regressions with 250 day window. Note: The perforated lines represents a 5% level of significance."
#| fig-height: 6
#| fig-width: 8
#| cache: true


CSAD_model_rol_gg <- general_herding$graphs$rol_gg
CSAD_model_rol_gg
```

\newpage
## US industry herding in periods of financial crises

```{r}
#| label: tbl-ols_crisis
#| tbl-cap: "Industry herding in crisis periods"
#| cache: true
#| include: true
#| eval: true

equation <-  as_equation(c("CSAD_{t} = \\gamma + \\gamma_1D^{crisis}|R_{m, t}| + \\gamma_2(1-D^{crisis})|R_{m, t}| + \\gamma_3D^{crisis}R_{m, t}^2 +  \\gamma_4(1-D^{crisis})R_{m, t}^2 +  \\epsilon_{t}"))
estimates <- c(
  "\\gamma",
  "\\gamma_1 ",
  "\\gamma_2",
  "\\gamma_3 ",
  "\\gamma_4"
)

CSAD_model_rol_crisis <- read_rds(here("Outputs", "artifacts_herding_crisis.rds"))
CSAD_model_rol_crisis_tbl <- CSAD_model_rol_crisis$models$combined_regression_tbl


CSAD_model_rol_crisis_tbl %>%
    ungroup() %>% 
  as_grouped_data(groups = c("Crisis")) %>% 
    as_flextable(hide_grouplabel = TRUE) %>%  
   mk_par(i =, j = 1, part = "header", value = as_paragraph("Industry")) %>% 
   mk_par(i =, j = c(2, 3, 4, 5, 6), part = "header", value = as_paragraph(as_equation(estimates))) %>% 
    add_footer_row(values = as_paragraph("Note: *** = p value < 0.01, ** = 0.01 < p value < 0.05, * = 0.05 < p value < 0.1."," ", " The regressions are based on ", equation), colwidths = 6) %>% 
  hline_bottom(part = "footer", border = fp_border(color = "black", style = "solid", width = 1)) %>% 
  align(j = 1, align = "left", part = "all") %>% 
  merge_at(i = 1) %>% 
  align(i = 1, align = "center") %>% 
  merge_at(i = 8) %>% 
  align(i = 8, align = "center") %>% 
  merge_at(i = 15) %>% 
  align(i = 15, align = "center") %>% 
  merge_at(i = 22) %>% 
  align(i = 22, align = "center") %>% 
  autofit(add_w = 0.1)


```

```{r}
#| label: fig-rol_crisis_gd
#| fig-cap: "Industry herding during the Great Depression using a 250-day rolling window. Note: The perforated lines represents a 5% level of significance."
#| fig-height: 6
#| fig-width: 8
#| cache: true

CSAD_model_rol_crisis$graphs$rol_gd_gg


```

```{r}
#| label: fig-rol_crisis_db
#| fig-cap: "Industry herding during the Dot-com Bubble using a 250-day rolling window. Note: The perforated lines represents a 5% level of significance."
#| fig-height: 6
#| fig-width: 8
#| cache: true

CSAD_model_rol_crisis$graphs$rol_db_gg
```

```{r}
#| label: fig-rol_crisis_fc
#| fig-cap: "Industry herding during the Financial Crisis using a 250-day rolling window. Note: The perforated lines represents a 5% level of significance."
#| fig-height: 6
#| fig-width: 8
#| cache: true

CSAD_model_rol_crisis$graphs$rol_fc_gg
```

```{r}
#| label: fig-rol_crisis_cv
#| fig-cap: "Industry herding during the Covid Crisis using a 250-day rolling window. Note: The perforated lines represents a 5% level of significance."
#| fig-height: 6
#| fig-width: 8
#| cache: true

CSAD_model_rol_crisis$graphs$rol_cv_gg
```


\newpage
## The role of fundamental information in US industry herding 

### In normal times

```{r}
#| label: tbl-ols_fund
#| tbl-cap: "Industry herding on fundamental information"
#| cache: true
#| include: true
#| eval: true

equation_1 <-  as_equation(c("CSAD_{NONFUND, t} = \\gamma + \\gamma_1R_{m, t}| + \\gamma_2R_{m, t}^2 + \\epsilon_{t}"))
equation_2 <-  as_equation(c("CSAD_{FUND, t} = \\gamma + \\gamma_1R_{m, t}| + \\gamma_2R_{m, t}^2 + \\epsilon_{t}"))
estimates <- c(
  "\\gamma",
  "\\gamma_1 ",
  "\\gamma_2"
)

CSAD_model_fundmamental <- read_rds(here("Outputs", "artifacts_fundamental_herding.rds"))
CSAD_model_fundamental_tbl <- CSAD_model_fundmamental$ols$ols_fund_tbl


CSAD_model_fundamental_tbl %>%
    ungroup() %>% 
  as_grouped_data(groups = c("Herd")) %>% 
    as_flextable(hide_grouplabel = TRUE) %>% 
   mk_par(i =, j = 1, part = "header", value = as_paragraph("Industry")) %>% 
   mk_par(i =, j = c(2, 3, 4), part = "header", value = as_paragraph(as_equation(estimates))) %>% 
    add_footer_row(values = as_paragraph("Note: *** = p value < 0.01, ** = 0.01 < p value < 0.05, * = 0.05 < p value < 0.1.", " ", " The regressions are based on ", equation_1, " and ", equation_2), colwidths = 4) %>% 
  hline_bottom(part = "footer", border = fp_border(color = "black", style = "solid", width = 1)) %>% 
  align(j = 1, align = "left", part = "all") %>% 
  merge_at(i = 1) %>% 
  align(i = 1, align = "center") %>% 
  merge_at(i = 8) %>% 
  align(i = 8, align = "center") %>% 
  autofit(add_w = 0.6)


```


```{r}
#| label: fig-rol_fundamental
#| fig-cap: "Industry herding on fundamental information using a 250-day rolling window. Note: The perforated lines represents a 5% level of significance."
#| fig-height: 6
#| fig-width: 8
#| cache: true

CSAD_model_fundmamental$ols_rol_graphs$rol_fundamental_gg

```


```{r}
#| label: fig-rol_nonfundamental
#| fig-cap: "Industry herding on non-fundamental information using a 250-day rolling window. Note: The perforated lines represents a 5% level of significance."
#| fig-height: 6
#| fig-width: 8
#| cache: true

CSAD_model_fundmamental$ols_rol_graphs$rol_nonfundamental_gg

```

### During crisis periods

\newpage

```{r}
#| label: tbl-ols_crisis_fund
#| tbl-cap: "Industry herding on fundamental information in crisis periods"
#| cache: true
#| include: true
#| eval: true

equation <-  as_equation(c("CSAD_{FUND, t} = \\gamma + \\gamma_1D^{crisis}|R_{m, t}| + \\gamma_2(1-D^{crisis})|R_{m, t}| + \\gamma_3D^{crisis}R_{m, t}^2 +  \\gamma_4(1-D^{crisis})R_{m, t}^2 +  \\epsilon_{t}"))

equation_2 <-  as_equation(c("CSAD_{NONFUND, t} = \\gamma + \\gamma_1D^{crisis}|R_{m, t}| + \\gamma_2(1-D^{crisis})|R_{m, t}| + \\gamma_3D^{crisis}R_{m, t}^2 +  \\gamma_4(1-D^{crisis})R_{m, t}^2 +  \\epsilon_{t}"))
estimates <- c(
  "\\gamma",
  "\\gamma_1 ",
  "\\gamma_2",
  "\\gamma_3 ",
  "\\gamma_4"
)

CSAD_model_rol_crisis_fund <- read_rds(here("Outputs", "artifacts_crisis_fundamental.rds"))
CSAD_model_rol_crisis_fund_tbl <- CSAD_model_rol_crisis_fund$ols$ols_tbl


CSAD_model_rol_crisis_fund_tbl %>%
    ungroup() %>% 
  as_grouped_data(groups = c("Fund")) %>% 
    as_flextable(hide_grouplabel = TRUE) %>%  
   mk_par(i =, j = 1, part = "header", value = as_paragraph("Industry")) %>% 
   mk_par(i =, j = c(2, 3, 4, 5, 6), part = "header", value = as_paragraph(as_equation(estimates))) %>% 
    add_footer_row(values = as_paragraph("Note: *** = p value < 0.01, ** = 0.01 < p value < 0.05, * = 0.05 < p value < 0.1.", " ", " The regressions are based on ", equation, " and ", equation_2), colwidths = 6) %>% 
  hline_bottom(part = "footer", border = fp_border(color = "black", style = "solid", width = 1)) %>% 
  align(j = 1, align = "left", part = "all") %>% 
  merge_at(i = 1) %>% 
  align(i = 1, align = "center") %>% 
  merge_at(i = 8) %>% 
  align(i = 8, align = "center") %>% 
  merge_at(i = 15) %>% 
  align(i = 15, align = "center") %>% 
  merge_at(i = 22) %>% 
  align(i = 22, align = "center") %>% 
  merge_at(i = 29) %>% 
  align(i = 29, align = "center") %>% 
  merge_at(i = 36) %>% 
  align(i = 36, align = "center") %>% 
  merge_at(i = 43) %>% 
  align(i = 43, align = "center") %>% 
  merge_at(i = 50) %>% 
  align(i = 50, align = "center") %>% 
  autofit(add_w = 0.1)


```



```{r}
#| label: fig-rol_fundamental_gd
#| fig-cap: "Industry herding on fundamental information during the Great depression using a 250-day rolling window. Note: The perforated lines represents a 5% level of significance."
#| fig-height: 6
#| fig-width: 8
#| cache: true

crisis_fundamental <- read_rds(here("Outputs", "artifacts_crisis_fundamental.rds"))

crisis_fundamental$fundamental$rol_fund_gd_gg
```


```{r}
#| label: fig-rol_fundamental_db
#| fig-cap: "Industry herding on fundamental information during the Dot-com bubble using a 250-day rolling window. Note: The perforated lines represents a 5% level of significance."
#| fig-height: 6
#| fig-width: 8
#| cache: true

crisis_fundamental$fundamental$rol_fund_db_gg
```


```{r}
#| label: fig-rol_fundamental_fc
#| fig-cap: "Industry herding on fundamental information during the Financial crisis using a 250-day rolling window. Note: The perforated lines represents a 5% level of significance."
#| fig-height: 6
#| fig-width: 8
#| cache: true

crisis_fundamental$fundamental$rol_fund_fc_gg
```


```{r}
#| label: fig-rol_fundamental_cv
#| fig-cap: "Industry herding on fundamental information during the Covid crisis using a 250-day rolling window. Note: The perforated lines represents a 5% level of significance."
#| fig-height: 6
#| fig-width: 8
#| cache: true

crisis_fundamental$fundamental$rol_fund_cv_gg
```


```{r}
#| label: fig-rol_nonfundamental_gd
#| fig-cap: "Industry herding on non-fundamental information during the Great depression using a 250-day rolling window. Note: The perforated lines represents a 5% level of significance."
#| fig-height: 6
#| fig-width: 8
#| cache: true

crisis_fundamental$nonfundamental$rol_nonfund_gd_gg
```


```{r}
#| label: fig-rol_nonfundamental_db
#| fig-cap: "Industry herding on non-fundamental information during the Dot-com bubble using a 250-day rolling window. Note: The perforated lines represents a 5% level of significance."
#| fig-height: 6
#| fig-width: 8
#| cache: true

crisis_fundamental$nonfundamental$rol_nonfund_db_gg
```


```{r}
#| label: fig-rol_nonfundamental_fc
#| fig-cap: "Industry herding on non-fundamental information during the Financial crisis using a 250-day rolling window. Note: The perforated lines represents a 5% level of significance."
#| fig-height: 6
#| fig-width: 8
#| cache: true

crisis_fundamental$nonfundamental$rol_nonfund_fc_gg
```


```{r}
#| label: fig-rol_nonfundamental_cv
#| fig-cap: "Industry herding on non-fundamental information during the Covid crisis using a 250-day rolling window. Note: The perforated lines represents a 5% level of significance."
#| fig-height: 6
#| fig-width: 8
#| cache: true

crisis_fundamental$nonfundamental$rol_nonfund_cv_gg
```

\newpage
##  Industry herding and political cycles

```{r}
#| label: tbl-political
#| tbl-cap: "Herding and political cycles."
#| cache: true

equation_1 <-
  as_equation(
    c(
      "Pr(D^{herd} = 1 | \\lambda_0 +  \\lambda_1D^{party}  + \\lambda_2\\Gamma_{t}) = \\lambda_0 +  \\lambda_1D^{party}  + \\lambda_2\\Gamma_{t}"
    ),
    height = 0.05,
    unit = "cm"
  )

equation_2 <-
  as_equation(
    c(
      "Pr(D^{herd}_{FUND} = 1 | \\lambda_0 + \\lambda_1D^{party} + \\lambda_2\\Gamma_{t}) = \\lambda_0 +  \\lambda_1D^{party} + \\lambda_2\\Gamma_{t}"
    ),
    height = 0.05,
    unit = "cm"
  )

equation_3 <-
  as_equation(
    c(
      "Pr(D^{herd}_{NONFUND} = 1 | \\lambda_0 +  \\lambda_1D^{party} + \\lambda_2\\Gamma_{t}) = \\lambda_0 +  \\lambda_1D^{party} + \\lambda_2\\Gamma_{t}"
    ),
    height = 0.05,
    unit = "cm"
  )

estimates <- c("\\lambda_0", "\\lambda_1", "\\lambda_2")

political <- read_rds(here("Outputs", "artifacts_party_dummy.rds"))
political$ols_party_dummy_model_tbl %>% 
  relocate(3, .before  = 2) %>% 
  ungroup() %>% 
  as_grouped_data(groups = c("Group")) %>% 
    as_flextable(hide_grouplabel = TRUE) %>% 
  mk_par(i =, j = 1, part = "header", value = as_paragraph("Industry")) %>% 
  mk_par(i =, j = c(2, 3, 4), part = "header", value = as_paragraph(as_equation(estimates))) %>%
  add_footer_lines(values = as_paragraph("Note: *** = p value < 0.01, ** = 0.01 < p value < 0.05, * = 0.05 < p value < 0.1.", 
                                       " The regressions are based on ", equation_1,
                                       " , ",
                                       equation_2,
                                       " and ",
                                       equation_3)) %>%
  hline_bottom(part = "footer",  
               border = fp_border(
                 color = "black",
                 style = "solid",
                 width = 1
               )) %>% 
  align(j = 1, align = "left", part = "all") %>% 
  merge_at(i = 1) %>% 
  align(i = 1, align = "center") %>% 
  merge_at(i = 8) %>% 
  align(i = 8, align = "center") %>% 
  merge_at(i = 15) %>% 
  align(i = 15, align = "center") %>%
  autofit(add_w = 0.6)
  
```

# Conclusion

\newpage


# References {.unnumbered}
::: {#refs}
:::


\setcounter{section}{0}
\renewcommand{\thesection}{\Alph{section}}

\setcounter{table}{0}
\renewcommand{\thetable}{A\arabic{table}}

\setcounter{figure}{0}
\renewcommand{\thefigure}{A\arabic{figure}}

\newpage

# Appendix

## Industry data

```{r}
#| label: fig-cons
#| fig-cap: "Consumables returns"
#| fig-height: 6
#| fig-width: 6
#| cache: true

returns_data <- read_rds(here("Outputs", "artifacts_returns_data.rds"))
returns_data$graphs$Consumer_durables_nondurables_wholesale_retail_some_services_group_equal_gg
```

```{r}
#| label: fig-health
#| fig-cap: "Health returns"
#| fig-height: 3
#| fig-width: 6
#| cache: true

returns_data$graphs$healthcare_medical_equipment_and_drugs_group_equal_gg
```

```{r}
#| label: fig-manufacturing
#| fig-cap: "Manufacturing returns"
#| fig-height: 6
#| fig-width: 6
#| cache: true

returns_data$graphs$manufacturing_energy_utilities_group_equal_gg
```

```{r}
#| label: fig-business
#| fig-cap: "Business services returns"
#| fig-height: 4
#| fig-width: 6
#| cache: true

returns_data$graphs$business_equipment_telephone_and_television_transmission_group_equal_gg
```

```{r}
#| label: fig-mines
#| fig-cap: "Other returns"
#| fig-height: 8
#| fig-width: 8
#| cache: true

returns_data$graphs$mines_constr_bldmt_trans_hotels_bus_serv_entertainment_finance__group_equal_gg
```
\newpage

## Industry grouping

```{r}
#| label: tbl-grouping
#| tbl-cap: "Industry grouping using CRSP SICs"
#| tbl-colwidths: auto
#| cache: true

aggregation_scheme_tbl <- returns_data$full_data$aggregation_scheme_tbl
aggregation_scheme_tbl %>% 
  flextable() %>% 
  align(align = "left", part = "all") %>% 
  autofit(add_w = -0.1)
```

\newpage

## Crises periods

```{r}
#| label: tbl-crises_description
#| tbl-cap: "Crises periods. Source: Wikipedia (2023)"
#| cache: true

crisis_tbl <- 
  tibble(
  "Crisis" = c("Great Depression", "Dot-com Bubble", "Financial Crisis", "Covid Crisis"),
  "Start" = c("1929-01-01", "1997-01-01", "2007-01-01", "2020-01-01"),
  "End" = c("1939-12-31", "2003-12-31", "2009-12-31", "2021-12-31")
) 

crisis_tbl %>% 
  flextable() %>% 
  align(j = 1, align = "left", part = "all") %>% 
  autofit(add_w = 1.5)

```

\newpage
## Fama-French factors

```{r}
#| label: fig-famafrench
#| fig-cap: "Fama-French Factors"
#| cache: true

famafrench <- read_rds(here("Outputs", "artifacts_fama_french.rds"))
famafrench$graphs$fama_french_gg

```

\newpage
## Presidential terms

```{r}
#| label: tbl-terms
#| tbl-cap: "Presidential terms"
#| cache: true

# importing presidential terms
presidential_terms <- read_rds(here("Outputs", "artifacts_presidential_terms.rds"))
presential_terms_tbl <- 
  presidential_terms$terms_tbl %>% 
  filter(Term_start >= "1920-01-01") %>%
  rename(
    "Start" = "Term_start",
    "End" = "Term_end") %>% 
  mutate(
    "Start" = lubridate::year(Start),
    "End" = lubridate::year(End)
  )

# creating table of presidential terms
presential_terms_tbl %>% 
  flextable() %>% 
  align(j = 1, align = "left", part = "all") %>% 
  colformat_double(j = 2:3, digits = 0, big.mark = "") %>%
  autofit(add_w = 1.8)

```

\newpage
## Market volatility

```{r}    
#| label: fig-volatility
#| fig-cap: "Market volatility"
#| cache: true

volatility <- read_rds(here("Outputs", "artifacts_volatility.rds"))
volatility$graphs$volatility_gg


```

\newpage

## Probit estimation

```{r}
#| label: tbl-probit
#| tbl-cap: "Probit estimation (Marginal Effects)"
#| cache: true

equation_1 <-
  as_equation(
    c(
      "Pr(D^{herd} = 1 | \\lambda_0 +  \\lambda_1D^{party}  + \\lambda_2\\Gamma_{t}) = \\lambda_0 +  \\lambda_1D^{party}  + \\lambda_2\\Gamma_{t}"
    ),
    height = 0.05,
    unit = "cm"
  )

equation_2 <-
  as_equation(
    c(
      "Pr(D^{herd}_{FUND} = 1 | \\lambda_0 + \\lambda_1D^{party} + \\lambda_2\\Gamma_{t}) = \\lambda_0 +  \\lambda_1D^{party} + \\lambda_2\\Gamma_{t}"
    ),
    height = 0.05,
    unit = "cm"
  )

equation_3 <-
  as_equation(
    c(
      "Pr(D^{herd}_{NONFUND} = 1 | \\lambda_0 +  \\lambda_1D^{party} + \\lambda_2\\Gamma_{t}) = \\lambda_0 +  \\lambda_1D^{party} + \\lambda_2\\Gamma_{t}"
    ),
    height = 0.05,
    unit = "cm"
  )

estimates <- c("\\lambda_1", "\\lambda_2")

political$probit_party_dummy_model_tbl %>% 
  relocate(3, .before  = 2) %>% 
  ungroup() %>% 
  as_grouped_data(groups = c("Group")) %>% 
    as_flextable(hide_grouplabel = TRUE) %>% 
  mk_par(i =, j = 1, part = "header", value = as_paragraph("Industry")) %>% 
  mk_par(i =, j = c(2, 3), part = "header", value = as_paragraph(as_equation(estimates))) %>%
  add_footer_lines(values = as_paragraph("Note: *** = p value < 0.01, ** = 0.01 < p value < 0.05, * = 0.05 < p value < 0.1.", 
                                       " The marginal effects are based on probit estimations of ", equation_1,
                                       " , ",
                                       equation_2,
                                       " and ",
                                       equation_3)) %>%
  hline_bottom(part = "footer",  
               border = fp_border(
                 color = "black",
                 style = "solid",
                 width = 1
               )) %>% 
  align(j = 1, align = "left", part = "all") %>% 
  merge_at(i = 1) %>% 
  align(i = 1, align = "center") %>% 
  merge_at(i = 8) %>% 
  align(i = 8, align = "center") %>% 
  merge_at(i = 15) %>% 
  align(i = 15, align = "center") %>%
  autofit(add_w = 1)


```


